Make manuscript figures

### 2021-10-28 scripts/R/make_manuscript_figures.rmd
add spvl on tree figure

Load libraries
```{r}
library(ggtree)
library(ggplot2)
library(dplyr)
library(POUMM)
library(ape)
library(cowplot)

FIGDIR <- "figures"

@@

gv_name <- "Pathogen part of trait"
gh_name <- "Host part of trait"
e_name <- "Non-pathogen part of trait"
ehat_name <- "Estimated non-pathogen part of trait"
z_minus_zbar_name <- "Scaled trait value"
```

Load data
```{r}
accuracy_simulation_results <- read.delim("output/2021-08-31_estimator_accuracy_MLE.txt")
tpr_simulation_results <- read.delim("output/2021-08-31_GWAS_TPR_MLE.txt")
```

@@

Inferred phylogeny
```{r}

>>>>

Load libraries
```{r}
library(ggtree)
library(ggplot2)
library(dplyr)
library(POUMM)
library(ape)
library(cowplot)
library(treeio)

FIGDIR <- "figures"
OUTDIR <- "output"

@@

gv_name <- "Pathogen part of trait"
gh_name <- "Host part of trait"
e_name <- "Non-pathogen part of trait"
gvhat_name <- "Estimated pathogen part of trait"
ehat_name <- "Estimated non-pathogen part of trait"
z_minus_zbar_name <- "Scaled trait value"
```

Load data
```{r}
accuracy_simulation_results <- read.delim("output/2021-08-31_estimator_accuracy_MLE.txt")
tpr_simulation_results <- read.delim("output/2021-08-31_GWAS_TPR_MLE.txt")
tree <- ape::read.tree(file = paste(OUTDIR, "pathogen_no_outgroup.newick", sep = "/"))
traits <- read.csv(file = paste(OUTDIR, "poumm_corrected_traits.csv", sep = "/"))
tree <- treeio::full_join(tree, traits, by = "label")
```

@@

Inferred phylogeny
```{r}
legend_width <- 15

# Plot tree with tip colors by spVL components
legend_x_pos <- 0.99
legend_y_pos <- 0.45

v_tree <- ggtree(tree, ladderize = F) +
        geom_tippoint(aes(color = v.MWA)) +
        scale_color_viridis_c(
                option = "plasma",
                direction = -1,
                limits = c(min(traits$v.MWA), max(traits$v.MWA))) +
        theme(legend.position = "bottom") +
        guides(color = guide_colorbar(title.position="top", title.hjust = 0.5)) +
        labs(color = yulab.utils::str_wrap(gvhat_name, width = legend_width))

h_tree <- ggtree(tree, ladderize = F) +
        geom_tippoint(aes(color = h.MWA)) +
        scale_color_viridis_c() +
        theme(legend.position = "bottom") +
        guides(color = guide_colorbar(title.position="top", title.hjust = 0.5)) +
        labs(color = yulab.utils::str_wrap(ehat_name, width = legend_width))

spvl_tree_same_scale <- ggtree(tree, ladderize = F) +
        geom_tippoint(aes(color = trait)) +
        scale_color_viridis_c(
                option = "plasma",
                direction = -1,
                limits = c(min(traits$v.MWA), max(traits$v.MWA))) +
        theme(legend.position = "bottom") +
        guides(color = guide_colorbar(title.position="top", title.hjust = 0.5)) +
        labs(color = yulab.utils::str_wrap("Calculated spVL", width = legend_width)) +
        scale_fill_identity(name = '', guide = 'legend', labels = c('oob'))

png(file = paste(FIGDIR, "spvl_on_tree.png", sep = "/"),
    height = height, width = linewidth,
    units = "cm",
    res = 300)
plot_grid(v_tree + theme(legend.position = "none"),
          h_tree + theme(legend.position = "none"),
          spvl_tree_same_scale + theme(legend.position = "none"),
          get_legend(v_tree), get_legend(h_tree), get_legend(spvl_tree_same_scale),
          nrow = 2, align = "v", axis = "tb",
          rel_heights = c(3, 1))
dev.off()
```
